```latex
\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\usepackage{ragged2e}
\usepackage{hyperref}
\usepackage[left=0.75in, right=0.75in, top=0.5in, bottom=0.5in]{geometry}
\usepackage{fontawesome5} % For icons

% --- Custom Commands for Resume Styling ---
% Section header
\newcommand{\sectionheader}[1]{%
  \vspace{1.5ex}\noindent\textbf{\Large #1}%
  \par\rule{\textwidth}{0.8pt}\vspace{0.5ex}%
}

% Subheading for Job/Project titles (e.g., Role, Company | Location, Dates)
\newcommand{\subheading}[4]{%
  \vspace{0.5ex}\noindent\textbf{#1}\hfill\textbf{#2}\par%
  \noindent\textit{#3}\hfill\textit{#4}\par\vspace{-0.5ex}%
}

% Hyperlink styling for better print and PDF view
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=blue,
    pdftitle={Harsh Agarwal Resume},
    pdfauthor={Harsh Agarwal}
}

\begin{document}
\pagestyle{empty} % No page numbers

% --- Contact Information ---
\begin{center}
    \vspace{-0.2in}
    \textbf{\Huge Harsh Agarwal} \\
    \vspace{1pt}
    \small \faPhone\ +91-9330557076 \textbar \faEnvelope\ \href{mailto:harshagarwal81528@gmail.com}{harshagarwal81528@gmail.com} \textbar \faLinkedin\ \href{https://linkedin.com/in/harshagarwal963}{linkedin.com/in/harshagarwal963} \textbar \faGithub\ \href{https://github.com/Harsh0369}{github.com/Harsh0369}
\end{center}

% --- Summary ---
\sectionheader{Summary}
\begin{itemize}[leftmargin=*,noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
    \item Highly motivated and results-driven Full-Stack Developer with a strong foundation in MERN stack, data structures, and algorithms.
    \item Proven ability to build scalable backend architectures, optimize API performance, and develop real-time applications.
    \item Demonstrated strong technical problem-solving, system design acumen, practical debugging skills, and leadership through academic projects, open-source contributions, and hackathon achievements.
    \item Eager to leverage technical expertise and collaborative spirit in a challenging Software Development Engineer role.
\end{itemize}

% --- Skills ---
\sectionheader{Skills}
\begin{itemize}[leftmargin=*,noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
    \item \textbf{Languages:} Java, Python, C++, JavaScript, C
    \item \textbf{Frameworks:} Django, React.js, Express.js, React Native
    \item \textbf{Data Technologies:} Pandas, NumPy, Scikit-learn, MongoDB, Redis, PostgreSQL
    \item \textbf{Web Technologies:} REST APIs, GraphQL, WebSocket, Tailwind CSS
    \item \textbf{Tools:} Git, Docker, Firebase, Vite, Postman
\end{itemize}

% --- Experience ---
\sectionheader{Experience}
\subheading{FIST-TBI, IIT Patna}{Patna, India}
            {Fintech Research Intern}{June 2025 – July 2025}
\begin{itemize}[leftmargin=*,noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
    \item Researched payment solutions for Bihar startups under IIT guidance, analyzing fintech trends and emerging technologies in digital payment systems and blockchain integration.
    \item Contributed to backend development using Node.js and Python frameworks for emerging fintech companies, implementing secure APIs and database optimization.
\end{itemize}

\subheading{Karyakaram}{Remote}
            {Full-Stack Developer Intern}{June 2025 – Present}
\begin{itemize}[leftmargin=*,noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
    \item Built complete backend architecture for React Native event management platform using Express.js, PostgreSQL, and Socket.IO, focusing on real-time chat system for group and solo chats.
    \item Integrated Redux for state management and JWT authentication, tested 30+ REST API endpoints with comprehensive frontend-backend integration and error handling.
\end{itemize}

\subheading{Social Summer of Code}{Remote}
            {Open Source Contributor}{May 2025 – Present}
\begin{itemize}[leftmargin=*,noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
    \item Developed React.js event platform with venue search and filtering using JavaScript, implemented Redis caching to optimize API latency by 25\% and enhanced user experience.
\end{itemize}

\subheading{GirlScript Summer of Code}{Remote}
            {Backend Developer}{May 2024 – Sep. 2024}
\begin{itemize}[leftmargin=*,noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
    \item Accelerated Node.js API response by 40\% using Redis caching and MongoDB optimization.
    \item Secured 500+ Daily Active Users (DAU) with JWT authentication and rate limiting implementation.
\end{itemize}

% --- Projects ---
\sectionheader{Projects}
\subheading{Co.Lab: Real-Time Code Collaboration}{\href{https://github.com/Harsh0369/Co.Lab}{GitHub}}
            {MERN Stack, Gemini API, Web Containers}{2025}
\begin{itemize}[leftmargin=*,noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
    \item Developed multi-user editor with live code execution, Redis session management (0.5s authentication), and AI suggestions via Gemini API.
    \item Reduced debug time by 40\% for 100+ users with web container-based runtime for Python/JS.
\end{itemize}

\subheading{Cab Booking System}{\href{https://github.com/Harsh0369/Cab-Booking-System}{GitHub}}
            {MERN Stack, Mapbox API}{2024}
\begin{itemize}[leftmargin=*,noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
    \item Implemented core features including live tracking (98\% accuracy), a 2.3s booking flow, and Razorpay integration (99\% success).
\end{itemize}

\subheading{URL Shortener}{\href{https://github.com/Harsh0369/URL-Shortener}{GitHub}}
            {MERN Stack, Redis}{2024}
\begin{itemize}[leftmargin=*,noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
    \item Engineered for high performance with 50ms redirects, custom analytics dashboard, JWT authentication, and rate limiting.
\end{itemize}

% --- Education ---
\sectionheader{Education}
\subheading{Institute of Technology, Guru Ghasidas University (CU)}{Bilaspur, India}
            {Bachelor of Technology in Information Technology}{Oct. 2023 – Present}
\begin{itemize}[leftmargin=*,noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
    \item GPA: 8.37/10.0
    \item Coursework: Operating Systems, Data Structures, Algorithms, OOP in C++, Computer Architecture
\end{itemize}

% --- Awards ---
\sectionheader{Awards}
\begin{itemize}[leftmargin=*,noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
    \item \textbf{5th Position} – Code of Phoenix Hackathon (Sentiment Analysis Platform for Social Media Advisory) \hfill Feb. 2025
    \item \textbf{8th Position} – Level SuperMind Hackathon (Astrology-based User Query Advisory Platform) \hfill Jan. 2025
\end{itemize}

% --- Certifications ---
\sectionheader{Certifications}
\begin{itemize}[leftmargin=*,noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
    \item Postman API Expert – Postman Certification \hfill Oct. 2024
\end{itemize}

% --- Leadership & Volunteering ---
\sectionheader{Leadership \& Volunteering}
\begin{itemize}[leftmargin=*,noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
    \item \textbf{GFG Student Chapter} – Lead \hfill May 2025 – Present
    \item \textbf{Google Developers Group} – Web Development Executive \hfill 2024 – Present
    \item \textbf{NSS Volunteer} – National Service Scheme \hfill 2023 – Present
\end{itemize}

\end{document}
```